---
title: "What Factors Influence Whether a Terrorist Attack is Successful?"
author: "Pablo Dragnic"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center")
```

## Introduction

The Global Terrorism Database (GTD) records terrorist attacks worldwide from 1970 to 2020. This analysis focuses on **2019** and investigates what factors influence whether a terrorist attack is **successful or not**. According to the GTD codebook, the `success` variable is coded as `1` if the attack achieved its intended effect (e.g., bomb detonated, hostage taken, target killed), and `0` otherwise. This is distinct from strategic success it measures tactical completion.

We examine the following predictor variables:

- **Attack type** (`attacktype1`)
- **Weapon type** (`weaptype1`)
- **Target type** (`targtype1`)
- **Region** (`region`)
- **Suicide attack** (`suicide`)
- **Part of multiple incident** (`multiple`)

We use EDA, chi-square tests, and logistic regression to answer the research question.

---

## 1. Data Loading and Preparation

```{r load-data}
library(ggplot2)
library(ezids)
library(pROC)
library(dplyr)
library(knitr)

# Load full dataset and filter to 2019
gtd_full <- read.csv("TerrorData.csv")
terror2019 <- gtd_full[gtd_full$iyear == 2019, ]

# Select relevant columns
terror2019 <- terror2019[, c("success", "attacktype1", "weaptype1", "targtype1",
                              "region", "suicide", "multiple")]

# Convert to factors (numeric codes kept for models)
terror2019$success     <- as.factor(terror2019$success)
terror2019$attacktype1 <- as.factor(terror2019$attacktype1)
terror2019$weaptype1   <- as.factor(terror2019$weaptype1)
terror2019$targtype1   <- as.factor(terror2019$targtype1)
terror2019$region      <- as.factor(terror2019$region)
terror2019$suicide     <- as.factor(terror2019$suicide)
terror2019$multiple    <- as.factor(terror2019$multiple)

# Labeled versions for readable plots
attack_labels <- c("1"="Assassination","2"="Armed Assault","3"="Bombing/Explosion",
                   "4"="Hijacking","5"="Barricade Incident","6"="Kidnapping",
                   "7"="Facility Attack","8"="Unarmed Assault","9"="Unknown")
weapon_labels <- c("1"="Biological","2"="Chemical","5"="Firearms","6"="Explosives",
                   "8"="Incendiary","9"="Melee","10"="Vehicle","11"="Sabotage",
                   "12"="Other","13"="Unknown")
region_labels <- c("1"="North America","2"="Cent. America & Caribbean",
                   "3"="South America","4"="East Asia","5"="Southeast Asia",
                   "6"="South Asia","7"="Central Asia","8"="Western Europe",
                   "9"="Eastern Europe","10"="Middle East & N. Africa",
                   "11"="Sub-Saharan Africa","12"="Australasia & Oceania")
targ_labels   <- c("1"="Business","2"="Government (General)","3"="Police",
                   "4"="Military","5"="Abortion Related","6"="Airports & Aircraft",
                   "7"="Government (Diplomatic)","8"="Educational Institution",
                   "9"="Food/Water Supply","10"="Journalists & Media",
                   "11"="Maritime","12"="NGO","13"="Other",
                   "14"="Private Citizens","15"="Religious","16"="Telecom",
                   "17"="Terrorists/Militias","18"="Tourists",
                   "19"="Transportation","20"="Unknown","21"="Utilities",
                   "22"="Violent Political Parties")

terror2019$attack_lbl <- attack_labels[as.character(terror2019$attacktype1)]
terror2019$weapon_lbl <- weapon_labels[as.character(terror2019$weaptype1)]
terror2019$region_lbl <- region_labels[as.character(terror2019$region)]
terror2019$targ_lbl   <- targ_labels[as.character(terror2019$targtype1)]

str(terror2019)
```

---

## 2. Exploratory Data Analysis

### 2.1 Overall Success Rate

```{r overall-success}
total    <- nrow(terror2019)
n_succ   <- sum(terror2019$success == 1)
n_unsucc <- sum(terror2019$success == 0)

cat("Total attacks in 2019:", total, "\n")
cat("Successful attacks:", n_succ, "(", round(n_succ/total*100, 1), "%)\n")
cat("Unsuccessful attacks:", n_unsucc, "(", round(n_unsucc/total*100, 1), "%)\n")
```

In 2019, the vast majority of recorded attacks were successful. The `success` variable is imbalanced, which we will keep in mind when interpreting model results.

```{r overall-plot}
ggplot(terror2019, aes(x = success, fill = success)) +
  geom_bar(color = "black", width = 0.5) +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5, size = 4) +
  scale_fill_manual(values = c("0" = "#d9534f", "1" = "#5cb85c"),
                    labels = c("Unsuccessful", "Successful")) +
  scale_x_discrete(labels = c("0" = "Unsuccessful", "1" = "Successful")) +
  labs(title = "Figure 1: Overall Attack Success in 2019",
       x = "Outcome", y = "Count", fill = "Outcome") +
  theme_minimal()
```

### 2.2 Success by Attack Type

```{r plot-attacktype}
ggplot(terror2019, aes(x = reorder(attack_lbl, table(attack_lbl)[attack_lbl]),
                       fill = success)) +
  geom_bar(position = "dodge", color = "black") +
  scale_fill_manual(values = c("0" = "#d9534f", "1" = "#5cb85c"),
                    labels = c("Unsuccessful", "Successful")) +
  coord_flip() +
  labs(title = "Figure 2: Attack Success by Attack Type",
       x = "Attack Type", y = "Count", fill = "Success") +
  theme_minimal()
```

### 2.3 Success by Weapon Type

```{r plot-weaptype}
ggplot(terror2019, aes(x = reorder(weapon_lbl, table(weapon_lbl)[weapon_lbl]),
                       fill = success)) +
  geom_bar(position = "dodge", color = "black") +
  scale_fill_manual(values = c("0" = "#d9534f", "1" = "#5cb85c"),
                    labels = c("Unsuccessful", "Successful")) +
  coord_flip() +
  labs(title = "Figure 3: Attack Success by Weapon Type",
       x = "Weapon Type", y = "Count", fill = "Success") +
  theme_minimal()
```

Weapon type codes: 1=Biological, 2=Chemical, 5=Firearms, 6=Explosives, 8=Incendiary, 9=Melee, 10=Vehicle, 11=Sabotage, 12=Other, 13=Unknown.

### 2.4 Success by Region

```{r plot-region}
ggplot(terror2019, aes(x = reorder(region_lbl, table(region_lbl)[region_lbl]),
                       fill = success)) +
  geom_bar(position = "dodge", color = "black") +
  scale_fill_manual(values = c("0" = "#d9534f", "1" = "#5cb85c"),
                    labels = c("Unsuccessful", "Successful")) +
  coord_flip() +
  labs(title = "Figure 4: Attack Success by Region",
       x = "Region", y = "Count", fill = "Success") +
  theme_minimal()
```

### 2.4b Success by Target Type

```{r plot-targtype}
ggplot(terror2019, aes(x = reorder(targ_lbl, table(targ_lbl)[targ_lbl]),
                       fill = success)) +
  geom_bar(position = "dodge", color = "black") +
  scale_fill_manual(values = c("0" = "#d9534f", "1" = "#5cb85c"),
                    labels = c("Unsuccessful", "Successful")) +
  coord_flip() +
  labs(title = "Figure 4b: Attack Success by Target Type",
       x = "Target Type", y = "Count", fill = "Success") +
  theme_minimal()
```

### 2.5 Success by Suicide Attack

```{r plot-suicide}
ggplot(terror2019, aes(x = suicide, fill = success)) +
  geom_bar(position = "dodge", color = "black") +
  scale_fill_manual(values = c("0" = "#d9534f", "1" = "#5cb85c"),
                    labels = c("Unsuccessful", "Successful")) +
  scale_x_discrete(labels = c("0" = "Non-Suicide", "1" = "Suicide")) +
  labs(title = "Figure 5: Attack Success by Suicide Attack Status",
       x = "Suicide Attack", y = "Count", fill = "Success") +
  theme_minimal()
```

### 2.6 Success by Multiple Incident

```{r plot-multiple}
ggplot(terror2019, aes(x = multiple, fill = success)) +
  geom_bar(position = "dodge", color = "black") +
  scale_fill_manual(values = c("0" = "#d9534f", "1" = "#5cb85c"),
                    labels = c("Unsuccessful", "Successful")) +
  scale_x_discrete(labels = c("0" = "Single", "1" = "Multiple")) +
  labs(title = "Figure 6: Attack Success by Part of Multiple Incident",
       x = "Part of Multiple Incident", y = "Count", fill = "Success") +
  theme_minimal()
```

---

## 3. Chi-Square Tests

For each predictor, we test whether it is independent of attack success. Alpha = 0.05 throughout.

### 3.1 Attack Type vs. Success

**H0:** Attack type and success are independent.  
**H1:** Attack type and success are not independent.

```{r chi-attacktype}
contable_att <- table(terror2019$success, terror2019$attacktype1)
xkabledply(contable_att, title = "Contingency Table: Success vs. Attack Type")
chisq.test(contable_att)
```

### 3.2 Weapon Type vs. Success

**H0:** Weapon type and success are independent.  
**H1:** Weapon type and success are not independent.

```{r chi-weaptype}
contable_wep <- table(terror2019$success, terror2019$weaptype1)
xkabledply(contable_wep, title = "Contingency Table: Success vs. Weapon Type")
chisq.test(contable_wep)
```

### 3.3 Target Type vs. Success

**H0:** Target type and success are independent.  
**H1:** Target type and success are not independent.

```{r chi-targtype}
contable_targ <- table(terror2019$success, terror2019$targtype1)
xkabledply(contable_targ, title = "Contingency Table: Success vs. Target Type")
chisq.test(contable_targ)
```

### 3.4 Region vs. Success

**H0:** Region and success are independent.  
**H1:** Region and success are not independent.

```{r chi-region}
contable_reg <- table(terror2019$success, terror2019$region)
xkabledply(contable_reg, title = "Contingency Table: Success vs. Region")
chisq.test(contable_reg)
```

### 3.5 Suicide vs. Success

**H0:** Suicide attack status and success are independent.  
**H1:** Suicide attack status and success are not independent.

```{r chi-suicide}
contable_sui <- table(terror2019$success, terror2019$suicide)
xkabledply(contable_sui, title = "Contingency Table: Success vs. Suicide")
chisq.test(contable_sui)
```

### 3.6 Multiple Incident vs. Success

**H0:** Part of multiple incident and success are independent.  
**H1:** Part of multiple incident and success are not independent.

```{r chi-multiple}
contable_mul <- table(terror2019$success, terror2019$multiple)
xkabledply(contable_mul, title = "Contingency Table: Success vs. Multiple Incident")
chisq.test(contable_mul)
```

---

## 4. Logistic Regression

Since `success` is a binary outcome, we use logistic regression (GLM with binomial family). We build and compare three models of increasing complexity. A helper function is defined to extract clean performance metrics from each model.

```{r helper-functions}
library(knitr)
library(kableExtra)

# Master label lookup: maps raw coefficient names -> readable labels
label_map <- c(
  "(Intercept)"    = "(Intercept)",
  # Attack type
  "attacktype12"   = "Attack: Armed Assault",
  "attacktype13"   = "Attack: Bombing/Explosion",
  "attacktype14"   = "Attack: Hijacking",
  "attacktype15"   = "Attack: Barricade Incident",
  "attacktype16"   = "Attack: Kidnapping",
  "attacktype17"   = "Attack: Facility Attack",
  "attacktype18"   = "Attack: Unarmed Assault",
  "attacktype19"   = "Attack: Unknown",
  # Weapon type
  "weaptype12"     = "Weapon: Chemical",
  "weaptype15"     = "Weapon: Firearms",
  "weaptype16"     = "Weapon: Explosives",
  "weaptype18"     = "Weapon: Incendiary",
  "weaptype19"     = "Weapon: Melee",
  "weaptype110"    = "Weapon: Vehicle",
  "weaptype111"    = "Weapon: Sabotage",
  "weaptype112"    = "Weapon: Other",
  "weaptype113"    = "Weapon: Unknown",
  # Target type
  "targtype12"     = "Target: Government (General)",
  "targtype13"     = "Target: Police",
  "targtype14"     = "Target: Military",
  "targtype15"     = "Target: Abortion Related",
  "targtype16"     = "Target: Airports & Aircraft",
  "targtype17"     = "Target: Government (Diplomatic)",
  "targtype18"     = "Target: Educational Institution",
  "targtype19"     = "Target: Food/Water Supply",
  "targtype110"    = "Target: Journalists & Media",
  "targtype111"    = "Target: Maritime",
  "targtype112"    = "Target: NGO",
  "targtype113"    = "Target: Other",
  "targtype114"    = "Target: Private Citizens",
  "targtype115"    = "Target: Religious",
  "targtype116"    = "Target: Telecom",
  "targtype117"    = "Target: Terrorists/Militias",
  "targtype118"    = "Target: Tourists",
  "targtype119"    = "Target: Transportation",
  "targtype120"    = "Target: Unknown",
  "targtype121"    = "Target: Utilities",
  "targtype122"    = "Target: Violent Political Parties",
  # Region
  "region2"        = "Region: Cent. America & Caribbean",
  "region3"        = "Region: South America",
  "region4"        = "Region: East Asia",
  "region5"        = "Region: Southeast Asia",
  "region6"        = "Region: South Asia",
  "region7"        = "Region: Central Asia",
  "region8"        = "Region: Western Europe",
  "region9"        = "Region: Eastern Europe",
  "region10"       = "Region: Middle East & N. Africa",
  "region11"       = "Region: Sub-Saharan Africa",
  "region12"       = "Region: Australasia & Oceania",
  # Suicide / multiple
  "suicide1"       = "Suicide Attack: Yes",
  "multiple1"      = "Part of Multiple Incident: Yes"
)

# Helper: formatted coefficient table with OR and 95% CI
coef_table <- function(model, title = "Coefficient Table") {
  s      <- summary(model)$coefficients
  or     <- exp(s[, 1])
  ci     <- exp(confint.default(model))
  df_out <- data.frame(
    Predictor    = ifelse(rownames(s) %in% names(label_map),
                          label_map[rownames(s)], rownames(s)),
    Coefficient  = round(s[, 1], 4),
    Std.Error    = round(s[, 2], 4),
    z.value      = round(s[, 3], 4),
    p.value      = round(s[, 4], 4),
    OR           = round(or, 4),
    CI_lower_95  = round(ci[, 1], 4),
    CI_upper_95  = round(ci[, 2], 4)
  )
  rownames(df_out) <- NULL
  kable(df_out, caption = title) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  full_width = FALSE, font_size = 12)
}

# Helper: confusion matrix metrics table (handles incomplete matrices)
conf_metrics <- function(pred, actual, model_name = "Model") {
  cm   <- table(factor(pred, levels = c(0,1)),
                factor(actual, levels = c(0,1)))
  TN   <- cm[1, 1]; FP <- cm[2, 1]
  FN   <- cm[1, 2]; TP <- cm[2, 2]
  acc  <- round((TP + TN) / sum(cm), 4)
  sens <- round(TP  / (TP + FN), 4)
  spec <- round(TN  / (TN + FP), 4)
  prec <- ifelse((TP + FP) == 0, NA, round(TP / (TP + FP), 4))
  f1   <- ifelse(is.na(prec), NA, round(2 * prec * sens / (prec + sens), 4))
  data.frame(Model       = model_name,
             Accuracy    = acc,
             Sensitivity = sens,
             Specificity = spec,
             Precision   = prec,
             F1_Score    = f1)
}
```

### 4.1 Model 1: Full Model (All Predictors)

```{r model1}
model1 <- glm(success ~ attacktype1 + weaptype1 + targtype1 + region + suicide + multiple,
              data = terror2019, family = binomial)
```

**Table 8: Coefficients, Odds Ratios, and 95% CI  Model 1**

```{r model1-coeftable, results='asis'}
coef_table(model1, title = "Table 8: Model 1  Coefficients, OR, and 95% CI")
```

**Confusion Matrix and Performance Metrics  Model 1:**

```{r model1-confusion}
probs1 <- predict(model1, type = "response")
pred1  <- ifelse(probs1 > 0.5, 1, 0)
cm1    <- table(Predicted = pred1, Actual = terror2019$success)
xkabledply(cm1, title = "Confusion Matrix  Model 1")
metrics1 <- conf_metrics(pred1, terror2019$success, "Model 1 (Full)")
kable(metrics1, caption = "Table 9: Performance Metrics  Model 1") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

**ROC Curve and AUC  Model 1:**

```{r model1-roc}
roc1  <- roc(terror2019$success, probs1)
plot(roc1, main = "Figure 7: ROC Curve  Model 1 (Full Model)")
best1 <- coords(roc1, "best", ret = c("threshold", "sensitivity", "specificity"),
                best.method = "youden")
kable(as.data.frame(best1), digits = 4,
      caption = "Table 10: Best Threshold (Youden)  Model 1") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
cat("AUC Model 1:", round(auc(roc1), 4), "\n")
```

---

### 4.2 Model 2: Reduced Model (Attack Type + Weapon Type + Region + Suicide)

```{r model2}
model2 <- glm(success ~ attacktype1 + weaptype1 + region + suicide,
              data = terror2019, family = binomial)
```

**Table 11: Coefficients, Odds Ratios, and 95% CI  Model 2**

```{r model2-coeftable, results='asis'}
coef_table(model2, title = "Table 11: Model 2  Coefficients, OR, and 95% CI")
```

**Confusion Matrix and Performance Metrics  Model 2:**

```{r model2-confusion}
probs2 <- predict(model2, type = "response")
pred2  <- ifelse(probs2 > 0.5, 1, 0)
cm2    <- table(Predicted = pred2, Actual = terror2019$success)
xkabledply(cm2, title = "Confusion Matrix  Model 2")
metrics2 <- conf_metrics(pred2, terror2019$success, "Model 2 (Reduced)")
kable(metrics2, caption = "Table 12: Performance Metrics Model 2") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

**ROC Curve and AUC Model 2:**

```{r model2-roc}
roc2  <- roc(terror2019$success, probs2)
plot(roc2, main = "Figure 8: ROC Curve Model 2 (Reduced Model)")
best2 <- coords(roc2, "best", ret = c("threshold", "sensitivity", "specificity"),
                best.method = "youden")
kable(as.data.frame(best2), digits = 4,
      caption = "Table 13: Best Threshold (Youden) Model 2") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
cat("AUC Model 2:", round(auc(roc2), 4), "\n")
```

---

### 4.3 Model 3: Minimal Model (Attack Type + Suicide)

```{r model3}
model3 <- glm(success ~ attacktype1 + suicide,
              data = terror2019, family = binomial)
```

**Table 14: Coefficients, Odds Ratios, and 95% CI Model 3**

```{r model3-coeftable, results='asis'}
coef_table(model3, title = "Table 14: Model 3 Coefficients, OR, and 95% CI")
```

**Confusion Matrix and Performance Metrics Model 3:**

```{r model3-confusion}
probs3 <- predict(model3, type = "response")
pred3  <- ifelse(probs3 > 0.5, 1, 0)
cm3    <- table(Predicted = pred3, Actual = terror2019$success)
xkabledply(cm3, title = "Confusion Matrix Model 3")
metrics3 <- conf_metrics(pred3, terror2019$success, "Model 3 (Minimal)")
kable(metrics3, caption = "Table 15: Performance Metrics Model 3") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

**ROC Curve and AUC Model 3:**

```{r model3-roc}
roc3  <- roc(terror2019$success, probs3)
plot(roc3, main = "Figure 9: ROC Curve Model 3 (Minimal Model)")
best3 <- coords(roc3, "best", ret = c("threshold", "sensitivity", "specificity"),
                best.method = "youden")
kable(as.data.frame(best3), digits = 4,
      caption = "Table 16: Best Threshold (Youden) Model 3") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
cat("AUC Model 3:", round(auc(roc3), 4), "\n")
```

---

## 5. Model Comparison

### 5.1 Likelihood Ratio Tests

```{r model-comparison}
null_dev <- model1$null.deviance
null_df  <- model1$df.null

p_m1    <- pchisq(null_dev - model1$deviance,
                  df = null_df - model1$df.residual, lower.tail = FALSE)
p_m2    <- pchisq(null_dev - model2$deviance,
                  df = null_df - model2$df.residual, lower.tail = FALSE)
p_m3    <- pchisq(null_dev - model3$deviance,
                  df = null_df - model3$df.residual, lower.tail = FALSE)
p_m1_m2 <- pchisq(model2$deviance - model1$deviance,
                   df = model2$df.residual - model1$df.residual, lower.tail = FALSE)
p_m2_m3 <- pchisq(model3$deviance - model2$deviance,
                   df = model3$df.residual - model2$df.residual, lower.tail = FALSE)

lrt_table <- data.frame(
  Comparison         = c("Model 1 vs Null", "Model 2 vs Null", "Model 3 vs Null",
                          "Model 1 vs Model 2", "Model 2 vs Model 3"),
  Chi_sq_statistic   = round(c(null_dev - model1$deviance,
                                null_dev - model2$deviance,
                                null_dev - model3$deviance,
                                model2$deviance - model1$deviance,
                                model3$deviance - model2$deviance), 2),
  df                 = c(null_df - model1$df.residual,
                          null_df - model2$df.residual,
                          null_df - model3$df.residual,
                          model2$df.residual - model1$df.residual,
                          model3$df.residual - model2$df.residual),
  p_value            = round(c(p_m1, p_m2, p_m3, p_m1_m2, p_m2_m3), 6)
)

kable(lrt_table, caption = "Table 17: Likelihood Ratio Tests Model Comparisons") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

### 5.2 Overall Model Performance Summary

```{r model-summary-table}
all_metrics <- rbind(metrics1, metrics2, metrics3)
all_metrics$AUC <- round(c(as.numeric(auc(roc1)),
                            as.numeric(auc(roc2)),
                            as.numeric(auc(roc3))), 4)
all_metrics$AIC <- round(c(AIC(model1), AIC(model2), AIC(model3)), 2)
all_metrics$Null_Deviance  <- round(c(model1$null.deviance,
                                       model2$null.deviance,
                                       model3$null.deviance), 2)
all_metrics$Resid_Deviance <- round(c(model1$deviance,
                                       model2$deviance,
                                       model3$deviance), 2)

kable(all_metrics,
      caption = "Table 18: Full Model Comparison Accuracy, AUC, AIC, Deviance") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  column_spec(2:8, bold = FALSE) %>%
  row_spec(which.max(all_metrics$AUC), bold = TRUE, color = "white", background = "#5cb85c")
```

The highlighted row indicates the best-performing model by AUC.

---

## 6. Odds Ratios Best Model

Based on AUC, AIC, and the likelihood ratio tests, we interpret odds ratios with 95% confidence intervals for the best-performing model (Model 2).

```{r odds-ratios}
or_vals <- exp(coef(model2))
ci_vals <- exp(confint.default(model2))

or_df <- data.frame(
  Predictor   = ifelse(names(or_vals) %in% names(label_map),
                       label_map[names(or_vals)], names(or_vals)),
  OR          = round(or_vals, 4),
  CI_lower_95 = round(ci_vals[, 1], 4),
  CI_upper_95 = round(ci_vals[, 2], 4)
)
rownames(or_df) <- NULL

kable(or_df, caption = "Table 19: Odds Ratios with 95% CI Model 2 (Best Model)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  row_spec(which(or_df$OR > 1 & or_df$CI_lower_95 > 1), background = "#d4edda") %>%
  row_spec(which(or_df$OR < 1 & or_df$CI_upper_95 < 1), background = "#f8d7da")
```

Rows highlighted in **green** indicate predictors that significantly *increase* the odds of success (OR > 1, CI entirely above 1). Rows in **red** indicate predictors that significantly *decrease* the odds of success.

---

## 7. Conclusions

Based on the 2019 GTD data (`r nrow(terror2019)` attacks), the chi-square tests indicate that **all six predictors**  attack type, weapon type, target type, region, suicide status, and whether the attack was part of a multiple incident  are statistically associated with attack success (all p-values < 0.05).

The logistic regression models confirm that **attack type** is the strongest and most consistent predictor of success. Suicide attacks are significantly more likely to succeed than non-suicide attacks, consistent with the attacker's commitment to completion. Region and weapon type also contribute meaningful predictive power, while target type and multiple incident status add less once other variables are controlled for.

Model 2 (attack type + weapon type + region + suicide) offers the best balance of fit and parsimony, with competitive AUC and accuracy relative to the full model.
```


