---
title: "Project2-EDA/logit-Aspen"
author: "Aspen Saplan"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r,echo=TRUE}
terror2019 = read.csv("TerrorData.csv")
terror2019 = terror2019[, c("property", "multiple", "weaptype1", "attacktype1", "imonth", "region")]
terror2019 = terror2019[terror2019$property != -9 & !is.na(terror2019$property),]
terror2019$property = as.factor(terror2019$property)
terror2019$multiple = as.factor(terror2019$multiple)
terror2019$weaptype1 = as.factor(terror2019$weaptype1)
terror2019$attacktype1 = as.factor(terror2019$attacktype1)
terror2019$imonth= as.factor(terror2019$imonth)
terror2019$region = as.factor(terror2019$region)
str(terror2019)
```


Number of records in 2019 with either property damage or no property damage:

```{r,echo=TRUE}
total = nrow(terror2019)
total
```

Number of records in 2019 without property damage:

```{r,echo=TRUE}
npd = sum(terror2019$property == 0)
npd
```

Number of records in 2019 with property damage:

```{r,echo=TRUE}
pd = sum(terror2019$property == 1)
pd
```

Percentage of records without property damage:

```{r,echo=TRUE}
(npd/total)
```

Percentage of records with property damage:
```{r,echo=TRUE}
(pd/total)
```


```{r,echo=TRUE}
library(ggplot2)
ggplot(terror2019, aes(x = multiple, fill = property)) +
  geom_bar(position = "dodge", color = "black")+
  scale_fill_manual(values = c(
    "1" = "purple",
    "0" = "red"
  ))+
  labs(title = "Count of Property Damage by Multiple Attacks",
    x = "Multiple",
    y = "Count of Property Damage",
    fill = "Property Damage")
```

```{r,echo=TRUE}
library(ggplot2)
ggplot(terror2019, aes(x = weaptype1, fill = property)) +
  geom_bar(position = "dodge", color = "black")+
  scale_fill_manual(values = c(
    "1" = "purple",
    "0" = "red"
  ))+
  labs(title = "Count of Property Damage by Weapon Type",
    x = "Weapon Type",
    y = "Count of Property Damage",
    fill = "Property Damage")
```

```{r,echo=TRUE}
library(ggplot2)
ggplot(terror2019, aes(x = attacktype1, fill = property)) +
  geom_bar(position = "dodge", color = "black")+
  scale_fill_manual(values = c(
    "1" = "purple",
    "0" = "red"
  ))+
  labs(title = "Count of Property Damage by Attack Type",
    x = "Attack Type",
    y = "Count of Property Damage",
    fill = "Property Damage")
```

```{r,echo=TRUE}
library(ggplot2)
ggplot(terror2019, aes(x = imonth, fill = property)) +
  geom_bar(position = "dodge", color = "black")+
  scale_fill_manual(values = c(
    "1" = "purple",
    "0" = "red"
  ))+
  labs(title = "Count of Property Damage by Month of Attack",
    x = "Month",
    y = "Count of Property Damage",
    fill = "Property Damage")
```

```{r,echo=TRUE}
library(ggplot2)
ggplot(terror2019, aes(x = region, fill = property)) +
  geom_bar(position = "dodge", color = "black")+
  scale_fill_manual(values = c(
    "1" = "purple",
    "0" = "red"
  ))+
  labs(title = "Count of Property Damage by Region of Attack",
    x = "Region",
    y = "Count of Property Damage",
    fill = "Property Damage")
```

Null Hypothesis: Multiple attacks and property damage are independent

Alternative Hypothesis: Multiple attacks and property damage are not independent

Alpha: 0.05

```{r,echo=TRUE}
library(ezids)
contableM = table(terror2019$property, terror2019$multiple)
xkabledply(contableM, title="Contingency table for property and multiple within dataset")
chitestM = chisq.test(contableM)
chitestM
```

Null Hypothesis: Weapon type and property damage are independent

Alternative Hypothesis: Weapon type and property damage are not independent

Alpha: 0.05

```{r,echo=TRUE}
library(ezids)
contableW = table(terror2019$property, terror2019$weaptype1)
xkabledply(contableW, title="Contingency table for property and weapon type within dataset")
chitestW = chisq.test(contableW)
chitestW
```

Null Hypothesis: Attack type and property damage are independent

Alternative Hypothesis: Attack type and property damage are not independent

Alpha: 0.05

```{r,echo=TRUE}
library(ezids)
contableA = table(terror2019$property, terror2019$attacktype1)
xkabledply(contableA, title="Contingency table for property and attack type within dataset")
chitestA = chisq.test(contableA)
chitestA
```

Null Hypothesis: Month of attack and property damage are independent

Alternative Hypothesis: Month of attack and property damage are not independent

Alpha: 0.05

```{r,echo=TRUE}
library(ezids)
contableMO = table(terror2019$property, terror2019$imonth)
xkabledply(contableMO, title="Contingency table for property and month of attack within dataset")
chitestMO = chisq.test(contableMO)
chitestMO
```

Null Hypothesis: Region of attack and property damage are independent

Alternative Hypothesis: Region of attack and property damage are not independent

Alpha: 0.05

```{r,echo=TRUE}
library(ezids)
contableR = table(terror2019$property, terror2019$region)
xkabledply(contableR, title="Contingency table for property and region of attack within dataset")
chitestR = chisq.test(contableR)
chitestR
```

```{r,echo=TRUE}
library(stats)
model1 = glm(property ~ multiple + attacktype1 + imonth + region + weaptype1, data = terror2019, family = binomial)
summary(model1)
```

```{r,echo=TRUE}
probs = predict(model1, type = "response")
pred = ifelse(probs > 0.5, 1, 0)
table(Predicted = pred, Actual= terror2019$property)
mean(pred == terror2019$property)
```
```{r,echo=TRUE}
library(pROC)
probs = predict(model1, type = "response")
r = roc(terror2019$property, probs)
plot(r)
auc(r)
best <- coords(r, "best", ret = c("threshold", "sensitivity", "specificity"), best.method = "youden")
best
```

```{r,echo=TRUE}
p1 = pchisq(8958.7 - 7069.4, df = 40, lower.tail = FALSE)
p1
```

```{r,echo=TRUE}
library(stats)
model2 = glm(property ~ multiple + attacktype1 + imonth, data = terror2019, family = binomial)
summary(model2)
```

```{r,echo=TRUE}
probs1 = predict(model2, type = "response")
pred1 = ifelse(probs1 > 0.5, 1, 0)
table(Predicted = pred1, Actual= terror2019$property)
mean(pred1 == terror2019$property)
```
```{r,echo=TRUE}
library(pROC)
probs1 = predict(model2, type = "response")
r = roc(terror2019$property, probs1)
plot(r)
auc(r)
best <- coords(r, "best", ret = c("threshold", "sensitivity", "specificity"), best.method = "youden")
best
```

```{r,echo=TRUE}
p1 = pchisq(8958.7 - 7616.2, df = 20, lower.tail = FALSE)
p1
```

```{r,echo=TRUE}
exp(coef(model2))
```
comparison model
```{r,echo=TRUE}
library(stats)
model3 = glm(property ~ multiple + attacktype1, data = terror2019, family = binomial)
summary(model3)
```
```{r,echo=TRUE}
probs2 = predict(model3, type = "response")
pred2 = ifelse(probs2 > 0.5, 1, 0)
table(Predicted = pred2, Actual= terror2019$property)
mean(pred2 == terror2019$property)
```

```{r,echo=TRUE}
library(pROC)
probs2 = predict(model3, type = "response")
r = roc(terror2019$property, probs2)
plot(r)
auc(r)
best <- coords(r, "best", ret = c("threshold", "sensitivity", "specificity"), best.method = "youden")
best
```

```{r,echo=TRUE}
p2 = pchisq(8958.7 - 7664.5, df = 11, lower.tail = FALSE)
p2
```